### 2022-11-16 files/Chapter7/Introduction.tex
Started with overview

In Section 7.2, the work in \cite{LVV09} is discussed and the numerical results are verified. In this article, the authors compare a cantilever Timoshenko beam to a cantilever two-dimensional beam. More results not given in  [LVV09] are also calculated, to be used in the sections following.

Section 7.3 is a natural extension of the article \cite{LVV09}. In this section, the validity of a two-dimensional beam model is investigated. The results of the two-dimensional beam are compared to a three-dimensional beam. The two-dimensional beam thus serves are an intermediate step to validate the Timoshenko beam model.

 extends the work of \cite{LVV09} to a comparison of a cantilever two-dimensional beam to a cantilever three-dimensional beam.\\

@@

\subsubsection{Parameters}
All the models in this dissertation are made of the same isotropic material and have square cross-section. Therefore for all the models, the elastic modulus $\displaystyle G = \frac{E}{2(1+\nu)}$. The shear correction factor is chosen as $\kappa^2 = 5/6$ and Poisson's ratio $\nu = 0.3$.\\

>>>>

In Section 7.2, the work in \cite{LVV09} is discussed and the numerical results are verified. In this article, the authors compare a cantilever Timoshenko beam to a cantilever two-dimensional beam. More results not given in  [LVV09] are also calculated, to be used in the sections following.\\

Section 7.3 is a natural extension of the article \cite{LVV09}. In this section, the validity of a two-dimensional beam model is investigated. The results of the two-dimensional beam are compared to a three-dimensional beam. The two-dimensional beam thus serves are an intermediate step to validate the Timoshenko beam model.\\

@@

\subsubsection{Global parameters}
All the models in this dissertation are made of the same isotropic material and have square cross-section. Therefore for all the models, the elastic modulus $\displaystyle G = \frac{E}{2(1+\nu)}$. The shear correction factor is chosen as $\kappa^2 = 5/6$ and Poisson's ratio $\nu = 0.3$.\\

### 2022-11-16 files/Overview.tex
Started with overview

\subsection{Introduction}

@@

\subsubsection{Introduction}

@@

@@

@@

\subsection{Introduction}

@@

\subsection{Introduction}

@@

@@

@@

\subsection{Introduction}

@@

@@

@@

@@

\subsection{Introduction}

@@

\subsection{Introduction}

>>>>

\section{Comparison of models}
\subsection{Model problem for a three-dimensional elastic solid}

Models for a three-dimensional elastic solid is presented. These models are a cantilever and a free-free elastic body. A dimensionless variational form of the cantilever model is derived. General plane stress is discussed.

@@

A model for a two-dimensional elastic solid is presented. The model is a cantilever elastic body. This model is a special case of plane stress of a three-dimensional elastic body. The model is given in a dimensionless variational form by simplification of the three-dimensional model.

@@

Models for a one-dimensional beam are presented using the Timoshenko beam theory. Four different models are presented. The models are a cantilever, free-free, pinned-pinned and a suspended beam. A dimensionless variational form for the models are derived.

@@

Models for a Reissner-Mindlin plate are presented. The models are a cantilever and a rigidly clamped plate. A dimensionless variational form for the cantilever model is derived.

\subsection{Rod Theory}
**************

@@

This chapter is a discussion and example of application of the theory presented in \cite{VV02}. This article concerns the existence and uniqueness of solutions of second order hyperbolic type problems. Like the models in this dissertation.\\

As an example to explain the theory, the a weak variational form of a cantilever Timoshenko beam is used.\\

This chapter also concerns the idea of modal analysis. This is a method to find the natural frequencies of a system. This method is used later in the dissertation.

@@

A general variational problem is defined. Specific Hilbert spaces are defined as well as notation. The four assumptions from \cite{VV02} is given.

\subsubsection{Main results for existence and uniqueness}
The main results from \cite{VV02} is presented. This includes cases for strong and weak damped systems. The models in this dissertation all have weak damping.

\subsubsection{First order system}
The general variational problem is rewritten for a first order system. To obtain this first order system, a operator $A$ is defined. The authors prove that this operator is a infinitesimal generator of a $C_0$-semigroup of contractions with a domain in the Hilbert space $H$.\\

The existence and uniqueness results for the first order system is easily proven with an initial value problem. The authors also prove that a solution of the first order system is also a solution to the general variational problem.

\subsection{Application: Timoshenko beam model}
The theory is applied to a cantilever Timoshenko beam model. Using the weak variational form, the four assumptions from \cite{VV02} is proven.

\subsection{Modal analysis}
*****************************************************************

\subsubsection{Timoshenko beam}
\subsubsection{General vibration problem}
\section{Finite element theory}

\subsection{Convergence of the Galerkin approximation}
In this chapter, two convergence results relating to the Finite Element Method is presented. The first result is a convergence result for the Galerkin approximation of a second order hyperbolic type problem. This is presented in \cite{BV13}.\\

The second result is from the textbook \cite{SF97}. This results concerns the convergence of the eigenvalues and eigenfunctions of a one-dimensional second order hyperbolic type problem when using the Finite Element Method.

\subsubsection{Galerkin approximation}
The general variational problem is identical to the one in \cite{VV02} presented in chapter 2. It is assumed that the the general variational problem has a unique solution.\\

The Galerkin approximation for the general variational problem is derived. Uniqueness of a solution to the Galerkin approximation is proven if $f$ is continuous.\\

@@

Continuing with to apply the Finite Element Method, the Galerkin approximation is rewritten as a system of ordinary differential equations. The system is a linear system.\\

\subsubsection{Error estimates}
Suppose $u$ is a solution to the general variational problem and $u^h$ is a solution to the Galerkin approximation. The goal of \cite{BV13} is to prove that $u^h$ converges to $u$ in $H$ as $h\rightarrow 0$.\\

A error estimate is defined by the authors. The error estimate is split into two parts. A semi-discrete part and a fully discrete part. The two parts are investigated separately.\\

@@

The main result of \cite{BV13} is presented. Two assumptions of \cite{BV13} are also given.

@@

In this subsection, the approach of the authors are discussed. First a error estimate for the semi-discrete problem is obtained.*****\\

\subsection{Convergence of eigenvalues in Finite Element Analysis}
*****************************************************************

\subsubsection{Eigenvalue problem for vibration problem}
\textbf{Problem GVarE}
\subsubsection{Interpolation theorem}
\subsubsection{Eigenvalue problem for our models*********}
\textbf{Notation}
\subsubsection{Convergence of the eigenvalues}
\subsubsection{Convergence of the eigenfunctions}
\subsection{Example}
\textbf{Problem 2D-1V}\\
\textbf{Test functions}
\subsubsection{Weak variational form}
\textbf{Problem 2D-1W}
\section{Timoshenko beam model}

In this chapter, the Timoshenko beam theory is explored further.

\subsection{Eigenvalue problem}
In the first three sections, the idea of modal analysis is applied to the Timoshenko beam theory. The first section follows the work of \cite{VV06}. In this article, the authors present a method of calculating the eigenvalues and eigenfunctions. 
\textbf{General eigenvalue problem}\\
\textbf{Case $\bm {\lambda <\alpha }$}\\
\textbf{Case $\bm { \lambda =\alpha }$}\\
\textbf{Case $\bm {\lambda >\alpha }$}
\subsection{Cantilever beam}
This is an example of the application of the theory on a cantilever Timoshenko beam.
\subsubsection{Calculating the eigenvalues}
\subsubsection{Example of mode shapes}
\subsection{Free-free timoshenko beam}

This is an example of the application of the theory on a free-free Timoshenko beam.

@@

The idea of a suspended Timoshenko is also discuss briefly.\\

@@

In the next section, an empirical study of the Timoshenko beam is discussed. In the article \cite{SP06} the authors obtained the eigenvalues of a Timoshenko beam, by analyzing the natural frequencies of a real world beam. Their findings are compared to various theoretical models.\\

@@

Last an example of the Timoshenko beam in application is presented. This section is a study of a technical report on a cantilever Timoshenko beam with elastic interfaces and a tip body.

@@

@@

******************************************************************\\
